---
title: "Data 605 HW 11"
author: "Yohannes Deboch"
date: "04/04/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Using the “cars” dataset in R, build a linear model for stopping distance as a function of speed and replicate the analysis of your textbook chapter 3 (visualization, quality evaluation of the model, and residual analysis.)

Answer:

## Load the libraries

```{r}
library(tidyverse)
```
## Get an overview of data
```{r}
glimpse(cars)
```
There are 50 observations and 2 variables . Speed and dist are double.

Summary Statistics

```{r}
summary(cars)
```

There are no outlier in the data. 

## Correlation between the variables
```{r}
cor(cars)
```

## Plot the data
```{r}
plot(cars$speed,cars$dist,type='p',main="Speed VS Distance")
```
The correlation between sped distance is strong and positive.

## Lienar Model
### Fit the model

We fitted a linear model of distance as a function f speed . Speed is the dependent and dist is the independent variable.

```{r}
fit <- lm(dist ~ speed, data = cars)
summary(fit)
```

Fitted regression model: $distance_{i} =  -17.5791 + 3.9324 * speed_{i}$

For 1 unit increase in speed distance traveled increases by 3.9324  units.
### Model Summary:
1. The model explains 65.11% variability in distance due to speed.
2. Speed is significant predictor of distance at 5% level of significant since the p value 1.49e-12 is less than 0.05.
3. The model is a valid model since the F statistics p value  1.49e-12 is less than 0.05 at 5% level of significance. 

## Residual Analysis

```{r}
par(mfrow=c(2,2))
plot(fit)
```

From the residual vs fitted value plot we can see the there is no pattern in the data hence the data randomness of the residuals and heteroscidatcity is satisfied.

From the normal q-q plot we can see that the residuals are Approximately normally distribute.

## Conclusion
From the overall analysis we can say that speed is a good predictor of distance and our model is a well fitted model since the assumptions of the linear regression model are satisfied here.
